Graph Exploration and Search

### 2017-11-13 paper.tex
Typos

Exploratory methods have been originally introduced as a mean to extract knowledge from relational data without knowing what to search~\cite{idreos2015overview}. 
Recently, \emph{graph exploration} has been introduced to perform exploratory analyses on graph-shaped data~\cite{mottin2017graph}. 
Graph exploration aims at mitigating the access to the data to the user, even if such user is a novice.

Algorithms for graph exploration assume the user is not able to completely specify the object of interest with  a structured query, like a SPARQL~\cite{prud2006sparql} query, but rather expresses the need with a simpler, more ambiguous language.

>>>>

Exploratory methods have been originally introduced as a mean to extract knowledge from relational data without knowing what to search~\citep{idreos2015overview}. 
Recently, \emph{graph exploration} has been introduced to perform exploratory analyses on graph-shaped data~\citep{mottin2017graph}. 
Graph exploration aims at mitigating the access to the data to the user, even if such user is a novice.

Algorithms for graph exploration assume the user is not able to completely specify the object of interest with  a structured query, like a SPARQL~\citep{prud2006sparql} query, but rather expresses the need with a simpler, more ambiguous language.
